Instability in Multi Agent Reinforcement Learning

### 2020-10-02 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
minor mods

\documentclass[sigconf]{aamas} 
%\documentclass[sigconf,anonymous]{aamas}

@@

@@

\begin{abstract}
Modelling the dynamics of Q-Learning is an active and important topic for the sake of developing an {\em a priori} understanding of Reinforcement Learning. In this paper, we use methods from evolutionary game theory to analyse the stability of Q-Learning in $p$-player games, where payoffs are randomly generated. We determine the parameter range in which Q-Learning is expected to settle to a stable fixed point and the range in which the dynamics are unstable.

This study allows for parameters to be appropriately chosen to ensure the safe convergence of a learning algorithm and as a first step towards understanding the range of behaviours that can be displayed by learning using the Q-Learning algorithm. We validate our theoretical results through numerical simulation and show that, within the bounds of experimental error, the region of instability can be characterised by the learning dynamics. We also note a few important implications of the study: 1) convergence is rare in Multi-Agent Reinforcement Learning. It is found that convergence to a unique fixed point occurs for simple games with 2 players and 2 actions. However, once either of these increase, convergence no longer occurs. 2) the existence of instability is not affected by the structure of the game itself. In fact, at least in the competitive regime, the payoff structure does not affect whether the game converges or not. 3) Convergence is guaranteed for low step-lengths but rapidly decreases as the step length increases. 
\end{abstract}

>>>>

%\documentclass[sigconf]{aamas} 
\documentclass[sigconf,anonymous]{aamas}

@@

\usepackage{xcolor} % REMOVE THIS AT THE END
\newcommand\fb[1]{\textcolor{blue}{FB: #1}}

\usepackage{soul}
\usepackage{subcaption}

@@

\begin{abstract}
Modelling the dynamics of Q-Learning is an active and important topic
for the sake of developing an {\em a priori} understanding of
Reinforcement Learning. In this paper, we use methods from
evolutionary game theory to analyse the stability of Q-Learning in
$p$-player games, where payoffs are randomly generated. We determine
the parameter range in which Q-Learning is expected to settle to a
stable fixed point and the range in which the dynamics are unstable.
%
This study allows for parameters to be appropriately chosen to ensure
the safe convergence of a learning algorithm.
%and as a first step
%towards understanding the range of behaviours that can be displayed by
%learning using the Q-Learning algorithm.
We validate our theoretical
results through numerical simulations and show that, within the bounds
of experimental error, the region of instability can be characterised
by the learning dynamics.
\fb{I think all of the following can be removed from the abstract:
We also note a few important implications of
the study: 1) convergence is rare in Multi-Agent Reinforcement
Learning. It is found that convergence to a unique fixed point occurs
for simple games with 2 players and 2 actions. However, once either of
these increase, convergence no longer occurs. 2) the existence of
instability is not affected by the structure of the game itself. In
fact, at least in the competitive regime, the payoff structure does
not affect whether the game converges or not. 3) Convergence is
guaranteed for low step-lengths but rapidly decreases as the step
length increases.
}
\end{abstract}
